RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-20 main.tex
:pencil: Update abstract

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}

\begin{document}
\title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
	}
}
\maketitle

@@

	% Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	% \gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	% \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
	% \gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
	\gls{bc} switches device load impedance to manipulate the magnitude, phase, and/or frequency responses for information modulation on the scattered carrier.
	% \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	% \gls{sr} allows the transmission of a primary node using active radio carrying primary information and of a secondary node scattering information onto primary signal, and the reception of information of both nodes.
	% \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
	% \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter, and employs a co-located receiver to decode both links.
	% \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
	\gls{sr} allows a passive scattering node to ride additional information over the primary radio emitted by an active transmitter, and employs a co-located receiver to decode both sources.
	% ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
	% \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
	% \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
	\gls{ris} programs an antenna/metamaterial array to adjust the scattering phase shifts for signal propagation control in specific directions.
	% and control signal strength in specific directions.
	% In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.

@@

	RIScatter is a new paradigm for future wireless networks and consists of multiple passive scattering nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.

@@

	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source, allowing universal hardware design and heterogeneous traffic control.

@@

	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed setup.
	We reveal RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.

@@

	An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by multiple RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter decision regions at the user.

@@

	Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming via smart input distribution design, which includes \gls{bc}, \gls{sr}, \gls{ris} as special cases.

@@

		As an emerging low-power communication technique, \gls{bc} separates conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		The node harvests energy from impinging wave and embeds information over scattered signal in a sustainable and controllable manner.
		% The backscatter reader can be either co-located or separated with the carrier emitter, known as monostatic and bistatic \gls{bc}.
		The backscatter reader can be either co-located or separated with the carrier emitter, known as \gls{mbc} and \gls{bbc} in Fig. \subref*{fi:mbc} and \subref*{fi:bbc}, respectively.

@@

		However, traditional \gls{bc} nodes only respond when externally inquired.
		In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals from legacy transmitters (e.g., radio, television and Wi-Fi) to harvest energy and establish connections.
		As illustrated in Fig. \subref*{fi:ambc}, it eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.
		To combat the strong direct-link interference of \gls{ambc}, \cite{Yang2018} proposed a co-located receiver that cooperatively decodes both primary (legacy) and backscatter links.

@@

		The concept of cooperative \gls{ambc} was further refined as \gls{sr} in Fig. \subref*{fi:sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.

@@

		In \gls{sr}, the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, while the co-located receiver decodes both links from both propagation paths.

@@

		On the other hand, \gls{ris} in Fig. \subref*{fi:ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
		With proper phase shift design, the scattered components can add constructively/destructively with the direct component for signal enhancement/interference suppression.

@@

		Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris} elements embed no additional information and use fixed reflection pattern over time, which can be optimized and fed back to the transmitter and receiver during coordination phase.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/mbc.tex}
				}
				\label{fi:mbc}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bbc.tex}
				}
				\label{fi:bbc}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambc.tex}
				}
				\label{fi:ambc}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/sr.tex}
				}
				\label{fi:sr}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ris.tex}
				}
				\label{fi:ris}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fi:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				% Paradigms for various scattering applications.
			}
			\label{fi:scatter_comparison}
		\end{figure}
	\end{subsection}

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (?ly collaborative)                        & 1                                       & 2 (adaptively collaborative)                      \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                     & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                     & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		To evaluate the performance of cooperative \gls{sr} receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, linear, and \gls{sic} detectors for flat fading channels, then proposed a low-complexity detector for frequency-selective fading channels.
		However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
		Although joint \gls{ml} decoding achieves the optimal detection performance for arbitrary backscatter-over-primary symbol period ratio, the computational complexity is prohibitive especially for high-order constellations \cite{Yang2018,Liang2020,Zhang2022}.
		For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
		If this ratio is sufficiently large, the authors proved the non-coherent primary achievable rate would approach its coherent counterpart asymptotically.
		This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
		However, the advantages of such \gls{sic} remain questionable as
		1) primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
		2) reflection pattern and signal characteristics are not fully exploited;
		3) non-coherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
		4) primary and backscatter symbols are superimposed by multiplication instead of superposition.

@@

	\begin{subsection}{Opportunities}
		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
		This question is answered in Section \ref{se:riscatter}.
	\end{subsection}
\end{section}

>>>>

% glossaries-extra
\setabbreviationstyle[acronym]{long-short}
\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bc}{BackCom}{Backscatter Communications}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bits per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bits per second per Hertz}
\newacronym{cp}{CP}{Canonical Polyadic}
\newacronym{cr}{CR}{Cognitive Radio}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{fdma}{FDMA}{Frequency-Division Multiple Access}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{ioe}{IoE}{Internet of Everything}
\newacronym{iot}{IoT}{Internet of Things}
\newacronym{kkt}{KKT}{Karush-Kuhn-Tucker}
\newacronym{m2m}{M2M}{Machine to Machine}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{mrt}{MRT}{Maximum Ratio Transmission}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{qos}{QoS}{Quality of Service}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{rfid}{RFID}{Radio-Frequency Identification}
\newacronym{ris}{RIS}{Reconfigurable Intelligent Surface}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{snr}{SNR}{Signal-to-Noise Ratio}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{swipt}{SWIPT}{Simultaneous Wireless Information and Power Transfer}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{ue}{UE}{user}
\newacronym{wit}{WIT}{Wireless Information Transfer}
\newacronym{wpcn}{WPCN}{Wireless Powered Communication Network}
\newacronym{wpt}{WPT}{Wireless Power Transfer}
\newacronym{mbc}{MBC}{Monostatic Backscatter Communications}
\newacronym{bbc}{BBC}{Bistatic Backscatter Communications}
\newacronym{bls}{BLS}{Backtracking Line Search}
\newacronym{mrc}{MRC}{Maximal Ratio Combining}
\newacronym{sdma}{SDMA}{Space-Division Multiple Access}
\newacronym{nlos}{NLoS}{Non-Line-of-Sight}
\newacronym{zf}{ZF}{Zero-Forcing}
\newacronym{mmse}{Minimum Mean-Square-Error}{MMSE}

\begin{document}
\title{RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface}
% \title{RIScatter: Unifying Backcatter Modulation and Passive Beamforming by Adaptive Input Distribution}
\author{
	\IEEEauthorblockN{
		Yang~Zhao,~\IEEEmembership{Member,~IEEE,}
		and~Bruno~Clerckx,~\IEEEmembership{Fellow,~IEEE}
	\thanks{
		The authors are with the Department of Electrical and Electronic Engineering, Imperial College London, London SW7 2AZ, U.K. (e-mail: \{yang.zhao18, b.clerckx\}@imperial.ac.uk).
\maketitle
% TODO why not use metamaterial? because high computational complexity and expectations of freedom (flexibility, reliability)
% TODO cooperative input design can be used for co-located RIScatter nodes.
% TODO hardward to modulate using RIS is already available.
% TODO RIScatter: enhance backscatter signal difference (suppress primary interference) or primary signal strength.
% TODO For Backscatter community: why not adaptive channel coding? For RIS community: why not add randomness for modulation?
% TODO RIS involves nonlinear circuits (e.g., diodes) and impedance design (i.e., perfect mismatching) is tricky for continuous phase shift; discrete candidate set is preferred (2-3 bits optimal)
% TODO Redefine RIS using book
% TODO Using RIS to encode is not very interesting as controller is anyway usable
% TODO Wi-Fi sampling rate 20 MHz (symbol period 50 nS), RFID symbol rate/load switching speed 100s KHz to 10s MHz [Backscatter Communications], fast load switching speed is key for high data rate - symbol ratio is not very large
% TODO Beamforming can cancel direct interference to avoid the collapse of non-coherent energy detection and enlarge energy gap.
% ? [Reconfigurable Intelligent Surface-Assisted Ambient Backscatter Communications Experimental Assessment]the authors of [5] show that, even in line-of-sight (LOS), the interferences and the desired signal can combine in such a way that the received signals at the reader side in the two states are close in power and only differ by their phases
% TODO Input probability distribution for discrete-value reflection (backscatter), constellation design for continue-value reflection (RIS)
% * TODO convergence
% TODO channel coding: general non-adaptive (book) adaptive (DMC)
% ? [Turbocharging] Since averaging must be done over a significant period of time to smooth out the variation in the TV transmissions, averaging does not allow rates much higher than 10 kbps [24].
% TODO mu-code: use multiple Rxs for noncoherent direct interference cancellation (instead of receive diversity)
% TODO backscatter modulation <-> passive beamforming; add adaptive channel coding over (NRZ) line coding.
% TODO semicoherent: known CSI, unknown primary/backscatter symbols
% TODO initialization, convergence
% TODO Base e, use 2 in simulation

@@

	% % Scatterers can harvest energy from, modulate information over, and influence propagation of surrounding radio waves.
	% % \gls{bc} varies object impedance to manipulate the magnitude, phase, and/or frequency of scattered signal to encode information and deliver within coverage.
	% % \gls{bc} switches load impedance that manipulates the magnitude, phase, and/or frequency responses to modulate information onto the scattered signal.
	% % \gls{bc} switches load impedance to manipulate the magnitude, phase, and/or frequency responses and modulate information onto the scattered signal.
	% \gls{bc} switches device load impedance to manipulate the magnitude, phase, and/or frequency responses for information modulation on the scattered carrier.
	% % \gls{sr} incorporates scatter nodes into active networks that recycle ambient signal to transmit self information and enhance legacy channel to the cooperative receiver.
	% % \gls{sr} allows the transmission of a primary node using active radio carrying primary information and of a secondary node scattering information onto primary signal, and the reception of information of both nodes.
	% % \gls{sr} introduces a passive scatterer that rides secondary information over the primary signal from an active transmitter, and employs a co-located receiver to sequentially decode both links.
	% % \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter, and employs a co-located receiver to decode both links.
	% % \gls{sr} introduces a passive scatterer to ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
	% \gls{sr} allows a passive scattering node to ride additional information over the primary radio emitted by an active transmitter, and employs a co-located receiver to decode both sources.
	% % ride secondary information over the primary radio from an active transmitter and employs a co-located receiver to decode both links.
	% % \gls{ris} adapts scattering antennas/programmable metamaterial to control wireless environment by varying signal strength in specific directions.
	% % \gls{ris} programs antenna/metamaterial array that adjusts the scattering phase shifts to control signal strength in specific directions.
	% \gls{ris} programs an antenna/metamaterial array to adjust the scattering phase shifts for signal propagation control in specific directions.
	% % and control signal strength in specific directions.
	% % In this paper, we depart from those concepts and introduce RIScatter as a new paradigm for future wireless networks.
	% \gls{bc} devices vary load impedance to modulate and reflect the signals
	% \gls{bc} nodes rely on dedicated carrier wave to
	% \gls{bc} nodes manipulate the magnitude, phase, and/or frequency responses to harvest energy from and modulate information over the carrier wave from a nearby emitter.
	\gls{bc} nodes harvest energy from and modulate information over an external carrier by manipulating the magnitude, phase, and/or frequency of the scattered signal.
	\gls{sr} incorporates a passive scatterer into existing radio networks to create additional propagation path and ride its own information for the cooperative receiver.
	\gls{ris} is a programmable reflector array that adapts the phase shift response to enhance or suppress signal strength in specific directions.

@@

	RIScatter is a new paradigm for future wireless networks and consists of multiple dispersed or co-located passive scattering nodes, whose reflection states can be adapted to partially engineer the wireless channel and partially modulate information onto the scattered wave.

@@

	The key principle in RIScatter is to render the probability distribution of reflection states as a joint function of the \gls{csi} and input information source for heterogeneous traffic control and universal hardware design.

@@

	This enables RISscatter to softly bridge, generalize, and outperform \gls{bc}, \gls{sr}, \gls{ris}; boil down to any of those under specific reflection states; or evolve in a mixed form.
	We show RIScatter provides a fundamental tradeoff that balances information modulation and channel reconfiguration capabilities in a flexible and mutualistic manner.

@@

	% For a typical scenario
	For a typical setup, we characterize the achievable primary-(total-)backscatter rate region by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.
	% An application scenario is considered where a multi-antenna \gls{ap} serves a single-antenna user surrounded by dispersed RIScatter nodes, and the achievable primary-total-backscatter rate region is characterized by optimizing input distribution at the nodes, active beamforming at the \gls{ap}, and backscatter detector at the user.

@@

	Simulation results demonstrate RIScatter nodes can exploit the additional propagation paths to smoothly transit between backscatter modulation and passive beamforming via smart input distribution design.

@@

		As an emerging low-power communication technique, \gls{bc} divides conventional transmitter into a \gls{rf} carrier emitter with power-hungry elements (e.g., synthesizer and amplifier) and an information-bearing node with power-efficient components (e.g., harvester and modulator) \cite{Boyer2014}.
		In particular, the node harvests energy from impinging wave and embeds information over scattered signal, while the backscatter reader can be either co-located or separated with the carrier emitter, shown as \gls{mbc} and \gls{bbc} in Fig. \subref*{fg:mbc} and \subref*{fg:bbc}, respectively.

@@

		However, conventional \gls{bc} nodes only respond when externally inquired by a nearby reader.
		To tackle this, \cite{Liu2013b} proposed an \gls{ambc} system where interactive nodes recycle ambient legacy signals (e.g., radio, television and Wi-Fi) to harvest energy and establish connections, as shown in Fig. \subref*{fg:ambc}.
		It eliminates the need of dedicated power supply, carrier emitter and frequency spectrum, but is subject to the strong direct-link interference.
		In \cite{Yang2018}, the authors proposed a cooperative \gls{ambc} system where both primary (legacy) and backscatter links are decoded at the same user under various detection schemes.
		% a cooperative receiver decodes both primary (legacy) and backscatter links using \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic}
		% co-located cooperative receiver to jointly or sequentially decode both primary (legacy) and backscatter links.

@@

		The concept of cooperative \gls{ambc} was further refined as \gls{sr} that cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}, which in shown Fig. \subref*{fg:sr}.
		% shown in Fig. \subref*{fg:sr}, which cognitively incorporates \gls{ambc} with existing systems \cite{Liang2020}.

@@

		% An illustration of \gls{sr} is shown in \subref*{fg:sr}, where the primary transmitter generates active radio and modulates primary information, the passive node scatters incoming wave and superimposes backscatter information, and the co-located receiver decodes both links from both propagation paths.
		In \gls{sr}, the active transmitter generates \gls{rf} wave carrying primary information, the passive node enhances the propagation environment and superimposes its own message on the scattered signal, and the cooperative receiver jointly or sequentially decodes both links.

@@

		% Above applications treat the scattering node as an information source.
		On the other hand, \gls{ris} is a smart planar reflector that consists of numerous low-power and low-cost elements with adjustable amplitude and phase responses.
		The reflection pattern over time is deterministic, which can be optimized and reported to the user before transmission.
		\gls{ris} recycles and redistributes surrounding \gls{rf} waves to customize wireless propagation environment for signal enhancement, interference suppression, scattering enrichment and non-line-of-sight bypassing \cite{Wu2021b}.
		% in Fig. \subref*{fg:ris} is a promising technology to recycle
		% On the other hand, \gls{ris} in Fig. \subref*{fg:ris} is a promising technology that evolves wireless propagation environment using numerous passive reflecting elements (e.g., scattering antenna or programmable metamaterial) with adjustable amplitudes and/or phases \cite{Wu2021b}.
		% With proper phase shift design, the scattered components can add constructively/destructively with the direct component for signal enhancement/interference suppression.

@@

		% Compared with scattering nodes of \gls{bc}/\gls{sr}, \gls{ris}
		% elements embed no additional information and use deterministic reflection pattern over time, which can be optimized and fed back to the transmitter and receiver during coordination phase.
		A comparison of different scattering applications is summarized in Table \ref{tb:scattering_applications}.

@@

		\begin{figure}[!t]
			\centering
			\subfloat[\gls{mbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/mbc.tex}
				}
				\label{fg:mbc}
			}
			\subfloat[\gls{bbc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/bbc.tex}
				}
				\label{fg:bbc}
			}
			\\
			\subfloat[\gls{ambc}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ambc.tex}
				}
				\label{fg:ambc}
			}
			\subfloat[\gls{sr}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/sr.tex}
				}
				\label{fg:sr}
			}
			\\
			\subfloat[\gls{ris}]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/ris.tex}
				}
				\label{fg:ris}
			}
			\subfloat[RIScatter]{
				\resizebox{0.48\linewidth}{!}{
					\input{assets/illustration/riscatter.tex}
				}
				\label{fg:riscatter}
			}
			\caption{
				Illustration of scattering applications.
				% Paradigms for various scattering applications.
			}
			\label{fg:scatter_comparison}
		\end{figure}
	\end{subsection}

	\begin{table*}[]
		\caption{Comparison of Scattering Applications}
		\label{tb:scattering_applications}
		\begin{tabularx}{\textwidth}{CCCCCCC}
			\toprule
			                              & \gls{mbc}                 & \gls{bbc}                 & \gls{ambc}                                      & \gls{sr}                                     & \gls{ris}                               & RIScatter                                         \\ \midrule
			Coexisting systems            & 1                         & 1                         & 2 (competitive)                                 & 2 (collaborative)                            & 1                                       & 2 (collaborative)                                 \\ \midrule
			Scatterer contribution        & Backscatter modulation    & Backscatter modulation    & Backscatter modulation and primary interference & Backscatter modulation and primary multipath & Passive beamforming                     & Backscatter modulation and passive beamforming    \\ \midrule
			Cooperative transmission      & ---                       & ---                       & No                                              & Active beamforming                           & ---                                     & Active beamforming and smart reflection           \\ \midrule
			Cooperative reception         & ---                       & ---                       & No (separated receivers)                        & Joint detection or \gls{sic}                 & ---                                     & Backscatter detection as primary channel training \\ \midrule
			Primary detection             & ---                       & ---                       & Semi-coherent                                   & Coherent or semi-coherent                    & Coherent                                & Coherent                                          \\ \midrule
			Backscatter detection         & Coherent                  & Coherent                  & Semi-coherent or noncoherent                    & Coherent                                     & ---                                     & Semi-coherent                                     \\ \midrule
			Reflection state distribution & Equiprobable (line-coded) & Equiprobable (line-coded) & Equiprobable (line-coded)                       & Equiprobable or Gaussian                     & Degenerate (\gls{csi}-adaptive)         & Flexible (\gls{csi}- and link priority-adaptive)  \\ \midrule
			Load-switching frequency      & Fast or slow              & Fast or slow              & Fast or slow                                    & Slow                                         & Slow (dynamic) or very slow (blockwise) & Fast or slow                                      \\ \bottomrule
		\end{tabularx}
	\end{table*}

	\begin{subsection}{Related Works}
		Similar to \gls{cr}, the coexistence of primary and backscatter links in \gls{sr} can be classified into commensal, parasitic, and competitive relationships, whose instantaneous rates, power schemes, and outage probabilities were acquired in \cite{Guo2019b,Ding2020}.
		To evaluate the performance of cooperative receivers, \cite{Yang2018} derived the bit error rates of \gls{ml}, \gls{mrc}, \gls{zf}, \gls{mmse} and \gls{sic} detectors for flat fading channels, and proposed a low-complexity detector for frequency-selective fading channels.
		However, it assumed equal symbol period of both links with perfect synchronization, which is impractical due to the load-switching speed constraint.
		Although joint \gls{ml} decoding achieves the optimal detection performance for arbitrary backscatter-over-primary symbol period ratio, the computational complexity is prohibitive especially for high-order constellations \cite{Yang2018,Liang2020,Zhang2022}.
		For sequential primary-backscatter decoding, the randomness of backscatter modulation can be modelled as either interference or channel uncertainty, depending on the symbol period ratio \cite{Long2020a}.
		If this ratio is sufficiently large, the authors proved the non-coherent primary achievable rate would approach its coherent counterpart asymptotically.
		This motivated \cite{Long2020a,Liang2020,Guo2019b,Ding2020,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022} to perform \gls{sic} from primary to backscatter links.
		However, the advantages of such \gls{sic} remain questionable as
		1) primary rate analysis is backed by long backscatter symbol period that constrains backscatter rate;
		2) reflection pattern and signal characteristics are not fully exploited;
		3) non-coherent primary encoding is required at the transmitter while re-encoding, precoding and subtraction are required at the receiver;
		4) primary and backscatter symbols are superimposed by multiplication instead of superposition.

@@

	\begin{subsection}{Opportunities}
		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
		This question is answered in Section \ref{st:riscatter}.
	\end{subsection}
\end{section}
